### 2019-08-27 manuscript/manuscript.tex
new figures

@@

With frequency collected at $T+1$ timepoints across $R$ replicate populations
at $L$ loci, we have $\mathbf{F}$ of allele frequencies, $\mathbf{D}$ array of
sequencing depths, and a $\mathbf{N}$ array of the number of individuals
sequenced, each of dimension $R \times (T+1) \times L$. We calculate the array
$\mathbf{\Delta F}$ which contains the allele frequency changes between
adjacent generations, and has dimension $R \times T \times L$. The operation
$\flt(\mathbf{\Delta}\mathbf{F})$ flattens this array to a $(R \cdot
T) \times L$ matrix, such that rows are grouped by replicate, e.g. for
timepoint $t$, replicate $r$, and locus $l$ and allele frequencies $p_{t, r}$,
for a single locus the entries are

@@

where each $\Delta p_{t, r, l} = p_{t+1, r, l} - p_{t, r, l}$. Then, the sample
temporal-replicate covariance matrix $\mathbf{Q}'$ calculated on
$\flt(\mathbf{\Delta F})$ is a $(R \cdot T) \times (R \cdot T)$
matrix. Given the bias of the sample covariance of allele frequency changes, we
calculated an expected bias matrix $\mathbf{B}$, averaging over loci,

@@

Thus, $\mathbf{B}$ is a $R \times (T+1)$ matrix. From XXX, we know that the
temporal variances and covariances require a correction,

>>>>

\begin{figure}[!ht]
  \centering
  \includegraphics[width=\textwidth]{figures/figure-2.pdf}
  \caption{}
  \label{}
\end{figure}

@@

With frequency collected at $T+1$ timepoints across $R$ replicate populations
at $L$ loci, we have $\mathbf{F}$ of allele frequencies, $\mathbf{D}$
multidimensional array of sequencing depths, and a $\mathbf{N}$
multidimensional array of the number of individuals sequenced, each of
dimension $R \times (T+1) \times L$.  We calculate the array $\mathbf{\Delta
F}$ which contains the allele frequency changes between adjacent generations,
and has dimension $R \times T \times L$.  The operation
$\flt(\mathbf{\Delta}\mathbf{F})$ flattens this array to a $(R \cdot T) \times
L$ matrix, such that rows are grouped by replicate, e.g. for timepoint $t$,
replicate $r$, and locus $l$ and allele frequencies $p_{t, r}$, for a single
locus the entries are

@@

where each $\Delta p_{t, r, l} = p_{t+1, r, l} - p_{t, r, l}$. Then, the sample
temporal-replicate covariance matrix $\mathbf{Q}'$ calculated on
$\flt(\mathbf{\Delta F})$ is a $(R \cdot T) \times (R \cdot T)$ matrix, with
the $R$ temporal-covariance block submatrices along the diagonal, and the
$R(R-1)$ replicate-covariance submatrices matrices in the upper and lower
triangles of the matrix,

\begin{align}
	\mathbf{Q}' &= 
  \begin{bmatrix} 
		\mathbf{Q}_{1,1}' & \mathbf{Q}_{1, 2}' & \ldots & \mathbf{Q}_{1, R}' \\ 
		\mathbf{Q}_{2,1}' & \mathbf{Q}_{2, 2}' & \ldots & \mathbf{Q}_{2, R}' \\ 
		\vdots & \vdots & \ddots & \vdots \\
		\mathbf{Q}_{R,1}' & \mathbf{Q}_{R, 2}' & \ldots & \mathbf{Q}_{R, R}' \\ 
  \end{bmatrix} 
\end{align}
%
where each submatrix $\mathbf{Q}_{i,j}'$ is the $T \times T$ sample covariance
matrix for replicates $i$ and $j$.

Given the bias of the sample covariance of allele frequency changes, we
calculated an expected bias matrix $\mathbf{B}$, averaging over loci,

@@

where division here is elementwise. Thus, $\mathbf{B}$ is a $R \times (T+1)$
matrix. As explained in XXX, each temporal covariance submatrix
$\mathbf{Q}_{r,r}$ requires two corrections.

\begin{equation}
	\[
	Q_{i,j} =  
		\begin{dcases}
			Q_{t,s}' - b_{t} - b_{s}, & \text{if  } t = s \\
			Q_{t,s}' + b_{}, & \text{if  } |i - j| = 1 \\
		\end{cases}
	\]
\end{equation}

$Q_{i,j} = \cov(\Delta p_i, \Delta p_j)$

Additionally, in some study designs, the frequencies from the first timepoint
